Learning and comparing functional connectomes across subjects

### 2012-12-30 paper.tex
Minor edits

%\title{Comparing Connectomes Between Populations}
\title{Learning and comparing functional connectomes between populations}

@@

% General introduction
Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
methodological challenges. Giving a picture of functional connectivity at
the subject level is by itself not straightforward, as the brain
comprises a myriad of interacting subsystems and must be decomposed in
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary
view is that of connections linking localized functional modules depicted
as a graph \cite{bullmore2009}. This representation of brain connectivity
is often called the functional connectome \cite{sporns2005} and is the
focus of intense worldwide research efforts as it holds promises of new
insights in cognition and pathologies
\cite{greicius2008b,biswal2010,fox2010}.

@@

>>>>

\title{Learning and comparing functional connectomes across subjects}

@@

% General introduction
Functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity
\cite{biswal1995,cordes2000}. Given that high-level
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while there exists a
well-defined standard analysis framework for activation mapping that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity still faces many open
methodological challenges. Giving a picture of functional connectivity at
the subject level is by itself not straightforward, as the brain
comprises a myriad of interacting subsystems and must be decomposed in
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary
view is that of connections linking localized functional modules depicted
as a graph \cite{bullmore2009}. This representation of brain connectivity
is often called the functional connectome \cite{sporns2005} and is the
focus of intense worldwide research efforts as it holds promises of new
insights in cognition and pathologies
\cite{greicius2008b,biswal2010,fox2010}.

@@

Horwitz \emph{el al.}\ \cite{horwitz1995} mentioned almost 20 years ago
that ``the crucial concept needed for network analysis is covariance''.
